Title

### 2019-05-08 4_method.tex
terminology considerations

>>>>

\hl{We need consistent terminology and symbols which adhere to standards in literature.}
The following synonym groups are used here which are not yet checked with existing literature':
\begin{itemize}
\item bones, medial axis segments, arms, fingers, ribs
\item joints, ticks, medial axis vertices, locations
\item MAT distance measure
\end{itemize}

Based on the straight skeleton naming, I would like to introduce a new consistent terminology:
\begin{itemize}
\item marked medial axis segment: vertebra
\item marked medial axis: spine
\item non-marked medial axis segment: arm
\item any medial axis segment: bone
\item bone introduced to the medial axis: rib
\item medial axis vert: joint
\item introduced medial axis vert: ligament?
\item location of an insets along a bone: tick? locus?
\end{itemize}
